Augraphy: An Augmentation Pipeline API for Modern Document Images

### 2023-01-17 paper.tex
fix image label, fix bibliography brackets, update pdf

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\hypersetup{
    colorlinks = false,
    linkbordercolor = {blue}
}
\usepackage{listings}
\usepackage{courier}
\usepackage{booktabs}
\usepackage[dvipsnames]{xcolor}
\usepackage{amssymb}
\usepackage{pifont}
\renewcommand{\floatpagefraction}{.8}

@@

@@

\section{Augraphy}
We were unable to find any tools for producing training images of modern documents, in a way suitable for automated use. The Augraphy library is our attempt at filling this gap.\\

The library contains 18 unique transformations — augmentations, in Augraphy's parlance — which may be sequenced into a pipeline object which carries out the image manipulation. Users of the library can define directed acyclic graphs of images and their transformations via the AugraphyPipeline API, representing the passage of a document through real-world alterations.\\

Augraphy attempts to decompose the lifetime of features accumulating in a document by separating the pipeline into three phases: ink, paper, and post. The ink phase exists to sequence effects which specifically alter the printed ink — like bleedthrough from too much ink on page, extraneous lines or regions from a mechanically faulty printer, or fading over time — and transform them prior to "printing". The paper phase is concerned with transformations of the underlying paper on which the ink gets printed; here we find the PaperFactory generator for creating a random texture from a set of given texture images, as well as effects like random noise, shadowing, watermarking, and staining. After the ink and paper textures are computed separately, they are merged in the manner of Technique 1 from the previous section, simulating the printing of the document. After "printing", the document enters the post-phase, wherein it may undergo alterations that would affect an already-printed document out in the world. Augmentations are available here which simulate the printed page being folded along multiple axes, marked by handwriting or highlighter, faxed, photocopied, scanned, photographed, burned, stained, and so on. Figure 1 shows the individual phases of an example pipeline combining to produce a noised document image.
\begin{figure}
\includegraphics[width=\textwidth]{pipeline.png}
\caption{Visualization of an Augraphy pipeline.} \label{fig1}
\end{figure}

\section{The Augraphy API}
The library was developed in Python, to allow maximal accessibility for practitioners, and was designed with an object-oriented structure, with concerns divided across a class hierarchy. When composed, different parts of the library interact to produce complex sequences of document image transformations, generating new synthetically-augmented datasets.\\

Modern frameworks for machine learning like \texttt{fastai} \cite{ref_fastai} aim to simplify the data handling requirements, and concordantly, the Augraphy development team takes great pains to ensure our library's ease-of-use and compatibility. We wanted the library to be immediately useful with little effort, especially as part of a preprocessing step for training machine learning models, so great care was taken to establish good defaults. The default Augraphy pipeline makes use of all of the augmentations available in Augraphy, with starting parameters selected after manual visual inspection of several thousand images. Adding a diverse array of realistic features to documents can be done with the following five-line incantation:
\begin{lstlisting}[language=Python]
from augraphy import *
pipeline = default_augraphy_pipeline()
img = cv2.imread("image.png")
data = pipeline.augment(img)
augmented_img = data["output"]
\end{lstlisting}

\subsection{Base}
\texttt{augraphy.base} is the core of the library, containing the central class for augmentations, another class for sequences of augmentations, and the pipeline class itself. The base classes exist to coordinate the compilation of discrete transformations into a larger pipeline, and to facilitate the operation and maintenance of these.\\

There are four ''main sequence'' classes in \texttt{augraphy.base}, which together provide the bulk of the library's functionality. Two additional classes, \texttt{OneOf} and \texttt{PaperFactory}, provide additional variation to pipelines in ways explored soon.

\subsubsection{Augmentation}
Augmentation is the most basic class in the project, and essentially exists as a thin wrapper over a probability value in the interval [0,1]. Every augmentation object is constructed with a probability of that augmentation being applied during the execution of a pipeline containing it.\\

This class also contains a method which interacts with the probability data, dynamically generating a second floating point probability value and using this to decide whether the augmentation should be applied at runtime.

\subsubsection{AugmentationResult}
After an augmentation is applied, the output of its execution is stored in an \texttt{AugmentationResult} object and passed forward through the pipeline. These objects also record an exact copy of the augmentation object that was instantiated and applied, as well as any metadata that might be relevant for debugging or other advanced use.

\subsubsection{AugmentationSequence}
A list of \texttt{Augmentation}s -- together with the intent to apply those Augmentations in sequence -- determines an \texttt{AugmentationSequence}, which is itself both an \texttt{Augmentation} and callable. In practice, these are the model for the pipeline phases discussed previously; they are essentially lists of \texttt{Augmentation} constructor calls which produce callable \texttt{Augmentation} objects of the various flavors explored in . \texttt{AugmentationSequences} are applied to the image during each of the \texttt{AugmentationPipeline} phases, and in each case yield the image, transformed by some of the Augmentations in the sequence.

\subsubsection{AugmentationPipeline}
The bulk of the innovation in Augraphy resides in the Augmentation pipeline, which is an abstraction over one or more events in a physical document's life. Events in this case could be the initial printing of the document when ink adhered to the paper material, or several weeks later when the document was adhered to a public board, annotated, defaced, and torn away from its securing staples. Fifty years later, our protagonist page resurfaces in the library archive during routine preservation-scanning efforts. Conservationists use delicate tools to gently position and record an image of the document, storing this in a public repository. An \texttt{AugmentationPipeline} can model this entire sequence of events, or any individual event within.\\

Realistically reproducing effects in document images requires rethinking how those effects are produced in the real world. Many issues, like the various forms of misprint, only affect text and images on the page. Others, like a coffee spill, change properties of the paper itself. Further still, there are transformations like physical deformations which alter the geometry and topology of both the page material and the graphical artifacts on it.\\

Effectively capturing processes like these in reproducible augmentations meant separating our model of a document augmentation pipeline into ink, paper, and post-processing layers, each containing some augmentations that modify the document image as it passes through. Augraphy pipelines, then, are constructed from three sequences of augmentations, to be applied one after the other in each of those phases. After transformations occur to the ink and to the paper separately, the pipeline fuses them together, simulating the printing of that ink on that paper. Changes to the document after that point happen within the post layer, where we might find effects like crumpling up the page and smoothing it out again, or using a pen to underline a section of text.\\

Use of the Augraphy library to produce a dataset for model training — will be covered in some detail later — boils down to the definition and application of one or more pipelines to one or more images.\\

@@

\subsubsection{OneOf}
Real-world processes generally allow for objects to exist in multiple states over time. To model the possibility that a document image has undergone one and only one of a collection of augmentations, we use \texttt{OneOf}, which simply selects one of those augmentations from a given list, and uses this to modify the image.

\subsubsection{PaperFactory}
We often print on multiple sizes and kinds of paper, and out in the world we certainly \textit{encounter} such diverse documents. We introduce this variation into the \texttt{AugmentationPipeline} by including \texttt{PaperFactory} in the \texttt{paper} phase of the pipeline. This augmentation checks a local directory for images of paper to crop, scale, and use as a background for the document image. The pipeline contains edge detection logic for lifting only text and other foreground objects from a clean image, greatly simplifying the "printing" onto another "sheet", and capturing in a reproducible way the construction method used to generate the NoisyOffice database. Taken together, \texttt{PaperFactory} makes it effectively possible to re-print a document onto other surfaces, like hemp paper, cardboard, or wood.

\subsection{Augmentations}
The \texttt{base} modules provide scaffolding for working with general transformations on document images, called \texttt{augmentations}. We have already included many such transforms in the standard library, and have also provided utilities for easily building new augmentations and integrating them into the Augraphy workflow.\\

Augraphy was designed to replicate effects seen in real-world documents in training data for image models, so each augmentation represents a feature that will appear in the final dataset. Augmentations come in many flavors and types, varying not only in their visual effect but also in their software design. Other libraries already exist for adding basic effects like blur, scaling, and rotation; Augraphy includes augmentations for these as well. The more interesting effects come from a combination of primitive effects, and mimic document types out in the world.\\

Figures 2 and 3 contain representative images of each augmentation applied to this very document. Descriptions of and motivation for each augmentation are available on GitHub \footnote{\url{https://github.com/sparkfish/augraphy}}.

@@

\subsection{Utilities}\label{utilities}
Interoperability and flexibility are core requirements of any data augmentation library, so Augraphy includes several utility classes designed to improve developer experience. Chief among these are \texttt{ComposePipelines}, \texttt{Foreign}, and \texttt{ImageOverlay}, which respectively

\begin{enumerate}
\item provide a means of composing two pipelines into one, allowing for the construction of complex pipeline algebras,
\item wrap augmentations from projects like \texttt{Albumentations} \cite{ref_albumentations} and \texttt{imgaug} \cite{ref_imgaug}, and
\item uses various blending algorithms to fuse foreground and background images together, useful for simulating "printing".
\end{enumerate}
\section{Deep Learning with Augraphy}
Augraphy aims to facilitate rapid dataset creation, advancing the state of the art for document image analysis tasks. This section describes a brief experiment using Augraphy to augment the NoisyOffice set, producing a corpus that is used to train a denoising convolutional neural network which outperforms an identically-structured model trained on only the provided NoisyOffice data. We continue to return to this database when testing our model training pipelines and new architectures, and felt it an appropriate jumping-off point for Augraphy analysis.

@@

\begin{figure}\label{fig4}
\includegraphics[width=\textwidth]{sidebyside.png}
\caption{Validation images (left), with the images predicted by the NoisyOffice (center) and Augraphy (right) models.} \label{fig4}
\end{figure}

>>>>

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\hypersetup{
    colorlinks = false,
    linkbordercolor = {blue}
}
\usepackage{listings}
\usepackage{courier}
\usepackage{booktabs}
\usepackage[dvipsnames]{xcolor}
\usepackage{amssymb}
\usepackage{pifont}
\usepackage{listings}
\usepackage{times}
\renewcommand{\floatpagefraction}{.8}

@@

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}
\lstset{style=mystyle}

@@

\section{Augraphy}
This section dives into detail about the \emph{Augraphy} library.
We first provide a high-level overview of the library, then discuss the various augmentations supported out-of-the-box, and finally discuss details of the structure of the library.

\subsection{Overview}

\emph{Augraphy} is a lightweight Python package for applying realistic perturbations to document images.
It is registered on the Python Package Index (PyPI) and can be installed using
\begin{center}
\textbf{\texttt{pip install augraphy}}
\end{center}
\emph{Augraphy} requires only a few other commonly-used Python scientific computing or image handling packages in order to run, such as NumPy \cite{numpy}. \emph{Augraphy} has been tested on Windows, Linux, and Mac computing environments. Listing \ref{lst:sample-code} shows how easy it is to get \emph{Augraphy} up and running to create a straightforward augmentation pipeline and apply it to an image:
%Examples of output generated by \emph{Augraphy} are shown in Figure~\ref{fig:augraphy_examples_3x5}.

\begin{lstlisting}[language=Python, label={lst:sample-code}, caption={Transforming an image with \emph{Augraphy}.}]
import augraphy; import cv2
pipeline = augraphy.default_augraphy_pipeline()
img = cv2.imread("image.png")
data = pipeline.augment(img)
augmented = data["output"]
\end{lstlisting}
Modern frameworks for machine learning like \emph{fastai} \cite{ref_fastai} aim to simplify the data handling requirements, and concordantly, the \emph{Augraphy} development team takes great pains to ensure our library's ease-of-use and compatibility.
%We wanted the library
The library is designed to be immediately useful with little effort, especially as part of a preprocessing step for training machine learning models, so great care was taken to establish good defaults.
The default \emph{Augraphy} pipeline (shown in the code snippet above) makes use of all of the augmentations available in \emph{Augraphy}, with starting parameters selected after manual visual inspection of several thousand images.

%We were unable to find any tools for producing training images of modern documents, in a way suitable for automated use. The Augraphy library is our attempt at filling this gap.\\

\emph{Augraphy} provides \numAugraphyAugmentations ~unique augmentations, which may be sequenced into a pipeline object that carries out the image manipulation.
Users of the library can define directed acyclic graphs of images and their transformations via the AugraphyPipeline API, representing the passage of a document through real-world alterations.
\emph{Augraphy} attempts to decompose the lifetime of features accumulating in a document by separating the pipeline into three phases: ink, paper, and post.
The ink phase exists to sequence effects which specifically alter the printed ink --- like bleedthrough from too much ink on page, extraneous lines or regions from a mechanically faulty printer, or fading over time --- and transform them prior to ``printing".

The paper phase is concerned with transformations of the underlying paper on which the ink gets printed; here, a \texttt{PaperFactory} generator is utilized for creating a random texture from a set of given texture images, as well as effects like random noise, shadowing, watermarking, and staining.
After the ink and paper textures are computed separately, they are merged in the manner of Technique 1 from the previous section, simulating the printing of the document.
After ``printing", the document enters the post phase, wherein it may undergo alterations that would affect an already-printed document out in the world.
Augmentations are available here which simulate the printed page being folded along multiple axes, marked by handwriting or highlighter, faxed, photocopied, scanned, photographed, burned, stained, and so on.
Figure~\ref{fig:pipeline} shows the individual phases of an example pipeline combining to produce a noised document image.

\begin{figure}
\centering
\scalebox{0.33}{
\includegraphics[]{pipeline.png}}
\caption{Visualization of an Augraphy pipeline, showing the composition of several image augmentations together with a specific paper background} \label{fig:pipeline}
\end{figure}

\subsection{Augraphy Augmentations}

Augraphy provides \numAugraphyAugmentations ~out-of-the-box augmentations.
These augmentations are listed in Table~\ref{tab:augmentations}.
As mentioned before, Ink Phase augmentations include those that imitate noisy processes that occur in a document's life cycle when ink is printed on paper.
These augmentations include \texttt{BleedThrough}, which imitates what happens when ink bleeds through from the opposite side of the page.
Another, \texttt{LowInkLines}, produces a streaking behavior common to printers running out of ink.

Augmentations provided by the Paper Phase include \texttt{BrightnessTexturize}, which introduces random noise in the brightness channel to emulate paper textures, and \texttt{Watermark}, which imitates watermarks in a piece of paper.
Finally, the Post Phase includes augmentations that imitate noisy-processes that occur after a document has been created.
These include \texttt{BadPhotoCopy}, which uses added noise to generate an effect of dirty copier, and \texttt{BookBinding}, which creates a book binding effect with shadow and curved lines to imitate how a page from a book might appear after being scanned with a flatbed scanner.
Other general-purpose augmentation libraries already exist for adding basic effects like blur, scaling, and rotation, but \emph{Augraphy} includes these types of augmentations as well.
Descriptions of- and motivation for each augmentation are available on GitHub. \footnote{\url{https://github.com/sparkfish/augraphy}}
% TODO: is there a more precise link for these descriptions?

%Augraphy is designed to replicate noise-like effects seen in real-world documents, and the library's
%, so each augmentation represents a feature that will appear in the final dataset.
%augmentations come in many flavors and types, varying not only in their visual effect but also in their software design.
%Other libraries already exist for adding basic effects like blur, scaling, and rotation; Augraphy includes augmentations for these as well. The more interesting effects come from a combination of primitive effects, and mimic document types out in the world.\\

% TODO: I don't think this table is entirely correct, some augmentations might be listed in the wrong columns
\begin{table}[]
    \centering
    \caption{Individual \emph{Augraphy} augmentations for each augmentation phase.}
    \scalebox{0.81}{
    \begin{tabular}{lll}
    \toprule
        \textbf{Ink Phase} & \textbf{Paper Phase} & \textbf{Post Phase} \\
        \midrule
        \textsf{BleedThrough} & \textsf{BrightnessTexturize} & \textsf{BadPhotoCopy} \\
        \textsf{DirtyDrum} & \textsf{ColorPaper} & \textsf{BindingsAndFasteners} \\
        \textsf{DirtyRollers} & \textsf{Gamma} & \textsf{BookBinding} \\
        \textsf{Dithering} & \textsf{Geometric} & \textsf{Folding} \\
        \textsf{Faxify} & \textsf{LightingGradient} & \textsf{JPEG} \\
        \textsf{InkBleed} & \textsf{PageBorder} & \textsf{NoiseTexturize} \\
        \textsf{Letterpress} & \textsf{SubtleNoise} & \textsf{Watermark} \\
        \textsf{LowInkLine} & & \\
        \textsf{Markup} & & \\
        \textsf{PencilScribbles} & & \\
        \bottomrule
    \end{tabular}}
    \label{tab:augmentations}
\end{table}

\subsection{The Augraphy Library}
\emph{Augraphy} is a Python-based library, allowing for maximal accessibility for practitioners,
%The library was developed in Python, to allow maximal accessibility for practitioners,
and is designed with an object-oriented structure, with concerns divided across a class hierarchy.
When composed, different parts of the library interact to produce complex sequences of document image transformations, generating new synthetically-augmented document images.

%Modern frameworks for machine learning like \emph{fastai} \cite{ref_fastai} aim to simplify the data handling requirements, and concordantly, the \emph{Augraphy} development team takes great pains to ensure our library's ease-of-use and compatibility.
%We wanted the library to be immediately useful with little effort, especially as part of a preprocessing step for training machine learning models, so great care was taken to establish good defaults.
%The default Augraphy pipeline makes use of all of the augmentations available in \emph{Augraphy}, with starting parameters selected after manual visual inspection of several thousand images.
%Adding a diverse array of realistic features to documents can be done with the following five-line incantation:
%\begin{lstlisting}[language=Python]
%from augraphy import *
%pipeline = default_augraphy_pipeline()
%img = cv2.imread("image.png")
%data = pipeline.augment(img)
%augmented_img = data["output"]
%\end{lstlisting}

%\subsection{Base}
%\texttt{augraphy.base} is the core of the library, containing the central class for augmentations, another class for sequences of augmentations, and the pipeline class itself. The base classes exist to coordinate the compilation of discrete transformations into a larger pipeline, and to facilitate the operation and maintenance of these.\\

%There are four ''main sequence'' classes in \texttt{augraphy.base}, which together provide the bulk of the library's functionality. Two additional classes, \texttt{OneOf} and \texttt{PaperFactory}, provide additional variation to pipelines in ways explored soon.

There are four ``main sequence" classes in the \emph{Augraphy} codebase, which together provide the bulk of the library's functionality.
%Two additional classes --- \texttt{OneOf} and \texttt{PaperFactory} --- provide additional variation to pipelines in ways 
We now discuss each of these:

%\subsubsection{Augmentation}
\smallskip
\noindent\textbf{\texttt{Augmentation}.} ~The \texttt{Augmentation} class is the most basic class in the project, and essentially exists as a thin wrapper over a probability value in the interval [0,1].
Every augmentation object is constructed with a probability of that augmentation being applied during the execution of a pipeline containing it.
This class also contains a method which interacts with the probability data, dynamically generating a second floating point probability value and using this to decide whether the augmentation should be applied at runtime.

%\subsubsection{AugmentationResult}
\smallskip
\noindent\textbf{\texttt{AugmentationResult}.} ~After an augmentation is applied, the output of its execution is stored in an \texttt{AugmentationResult} object and passed forward through the pipeline.
These objects also record an exact copy of the augmentation object that was instantiated and applied, as well as any metadata that might be relevant for debugging or other advanced use.

%\subsubsection{AugmentationSequence}
\smallskip
\noindent\textbf{\texttt{AugmentationSequence}.} ~A list of \texttt{Augmentation}s --- together with the intent to apply those Augmentations in sequence --- determines an \texttt{AugmentationSequence}, which is itself both an \texttt{Augmentation} and callable.
In practice, these are the model for the pipeline phases discussed previously; they are essentially lists of \texttt{Augmentation} constructor calls which produce callable \texttt{Augmentation} objects of the various flavors explored in \texttt{AugmentationSequences} are applied to the image during each of the \texttt{AugmentationPipeline} phases, and in each case yield the image, transformed by some of the Augmentations in the sequence.

%\subsubsection{AugmentationPipeline}
\smallskip
\noindent\textbf{\texttt{AugmentationPipeline}.} ~The bulk of the innovation in \emph{Augraphy} resides in the Augmentation pipeline, which is an abstraction over one or more events in a physical document's life.
Events in this case could be the initial printing of the document when ink adhered to the paper material, or several weeks later when the document was adhered to a public board, annotated, defaced, and torn away from its securing staples.
Fifty years later, our protagonist page resurfaces in the library archive during routine preservation-scanning efforts. Conservationists use delicate tools to gently position and record an image of the document, storing this in a public repository.
An \texttt{AugmentationPipeline} can model this entire sequence of events, or any individual event within.

Realistically reproducing effects in document images requires rethinking how those effects are produced in the real world.
Many issues, like the various forms of misprint, only affect text and images on the page.
Others, like a coffee spill, change properties of the paper itself. Further still, there are transformations like physical deformations which alter the geometry and topology of both the page material and the graphical artifacts on it.
Effectively capturing processes like these in reproducible augmentations means separating our model of a document augmentation pipeline into ink, paper, and post-processing layers, each containing some augmentations that modify the document image as it passes through.
ils down to the definition and application of one or more pipelines to one or more images.

@@

\smallskip
There are two additional classes that provide additional functionality in order to round out the \emph{Augraphy} library:

%\subsubsection{OneOf}
%\smallskip
\noindent\textbf{\texttt{OneOf}.} ~Real-world processes generally allow for objects to exist in multiple states over time.
To model the possibility that a document image has undergone one and only one of a collection of augmentations, we use \texttt{OneOf}, which simply selects one of those augmentations from a given list, and uses this to modify the image.

%\subsubsection{PaperFactory}
\smallskip
\noindent\textbf{\texttt{PaperFactory}.} ~We often print on multiple sizes and kinds of paper, and out in the world we certainly \textit{encounter} such diverse documents.
We introduce this variation into the \texttt{AugmentationPipeline} by including \texttt{PaperFactory} in the \texttt{paper} phase of the pipeline.
This augmentation checks a local directory for images of paper to crop, scale, and use as a background for the document image.
The pipeline contains edge detection logic for lifting only text and other foreground objects from a clean image, greatly simplifying the ``printing" onto another ``sheet", and capturing in a reproducible way the construction method used to generate the NoisyOffice database.
Taken together, \texttt{PaperFactory} makes it effectively possible to re-print a document onto other surfaces, like hemp paper, cardboard, or wood.

\smallskip
Interoperability and flexibility are core requirements of any data augmentation library, so \emph{Augraphy} includes several utility classes designed to improve developer experience:

%\smallskip
\noindent\textbf{\texttt{ComposePipelines}.} ~This class provides a means of composing two pipelines into one, allowing for the construction of complex pipeline algebras.

\smallskip
\noindent\textbf{\texttt{Foreign}.} ~This class can be used to wrap augmentations from external projects like \emph{Albumentations} and \emph{imgaug}.

\smallskip
\noindent\textbf{\texttt{ImageOverlay}.} ~This class uses various blending algorithms to fuse foreground and background images together, which is useful for simulating ``printing".

%\subsection{Augmentations}
%The \texttt{base} modules provide scaffolding for working with general transformations on document images, called \texttt{augmentations}. We have already included many such transforms in the standard library, and have also provided utilities for easily building new augmentations and integrating them into the Augraphy workflow.\\

%Augraphy was designed to replicate effects seen in real-world documents in training data for image models, so each augmentation represents a feature that will appear in the final dataset. Augmentations come in many flavors and types, varying not only in their visual effect but also in their software design. Other libraries already exist for adding basic effects like blur, scaling, and rotation; Augraphy includes augmentations for these as well. The more interesting effects come from a combination of primitive effects, and mimic document types out in the world.\\

%Figures 2 and 3 contain representative images of each augmentation applied to this very document. Descriptions of and motivation for each augmentation are available on GitHub \footnote{\url{https://github.com/sparkfish/augraphy}}.

@@

%\subsection{Utilities}\label{utilities}
%Interoperability and flexibility are core requirements of any data augmentation library, so Augraphy includes several utility classes designed to improve developer experience. Chief among these are \texttt{ComposePipelines}, \texttt{Foreign}, and \texttt{ImageOverlay}, which respectively

%\begin{enumerate}
%\item provide a means of composing two pipelines into one, allowing for the construction of complex pipeline algebras,
%\item wrap augmentations from projects like \texttt{Albumentations} \cite{ref_albumentations} and \texttt{imgaug} \cite{ref_imgaug}, and
%\item uses various blending algorithms to fuse foreground and background images together, useful for simulating "printing".
%\end{enumerate}
\emph{Augraphy} pipelines, then, are constructed from three sequences of augmentations, to be applied one after the other in each of those phases.
Afterch will be covered in some detail in the next section Î transformations occur to the ink and to the paper separately, the pipeline fuses them together, simulating the printing of that ink on that paper.
Changes to the document after that point happen within the post layer, where we might find effects like crumpling up the page and smoothing it out again, or using a pen to underline a section of text.
Use of the Augraphy library to produce a dataset for model training Î

\section{Deep Learning with Augraphy}
Augraphy aims to facilitate rapid dataset creation, advancing the state of the art for document image analysis tasks. This section describes a brief experiment using Augraphy to augment the NoisyOffice set, producing a corpus that is used to train a denoising convolutional neural network which outperforms an identically-structured model trained on only the provided NoisyOffice data. We continue to return to this database when testing our model training pipelines and new architectures, and felt it an appropriate jumping-off point for Augraphy analysis.

@@

\begin{figure}\label{fig4}
\includegraphics[width=\textwidth]{sidebyside.png}
\caption{Validation images (left), with the images predicted by the NoisyOffice (center) and Augraphy (right) models.}
\end{figure}
